%!TEX root = ../document.tex
\chapter{Project Organizational Structure}

\section{Project Organizational Chart}

The Flying Vehicle Design and Production project team consists of a project steering committee, a customer service team, a project manager, a functional team, and a technical team. The project was initiated by the Project Steering Committee, which is also the main decision maker and strategy maker for the project. All project matters are coordinated and managed by the project team. The project team will consist of full-time project managers, technicians, and business owners and experts in key functional areas.In addition, the project team will include technical and functional consultants from the client side.

{\color{red}{插图}}

\section{Responsibility}

The work of this project is completed by a project team composed of Ethane Autoplane Co.Ltd. and the client side, which means that the two parties form a common working group in the project to complete each project task. The main consideration of this arrangement is to ensure that the design and manufacturing of the flight and the car meet the customer's requirements during the project, and when necessary, communicate with the customer about the design details of the flying car, and coordinate the design between the designer and the customer. Only in this way can the order of the design and manufacturing of the flying car be guaranteed.

Specifically, the division of labor and responsibilities of Ethane Autoplane Co.Ltd and the client are:

\subsection{Project management team responsibilities}

\renewcommand\arraystretch{1.0}
\begin{longtable}{|m{3cm}<{\centering}|m{3cm}<{\centering}|m{8cm}<{\centering}|}
%\caption{\textbf{Project milestones}}

\label{tab:3-1}\\
\toprule
\textbf{Role} & \textbf{Personnel} & \textbf{Description} \\
\midrule
\endfirsthead
\multicolumn{3}{c}{Continued \autoref{tab:milestones}}\\
\multicolumn{3}{c}{(following last page)}\\
\toprule
\textbf{Role} & \textbf{Personnel} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\multicolumn{3}{c}{(continued on next page)}
\endfoot
\bottomrule
\endlastfoot

\footnotesize

\multirow{5}{*}{\bfseries \footnotesize Steering Committee Member/Project Director} & 
\multirow{5}{*}{\bfseries \footnotesize Related personnel} &   \\
\cline{3-3}
                         &   & Support and monitor project actions; \\
\cline{3-3}
                         &   & Review/approve the project plan with the leader; \\
\cline{3-3}
                         &   & Review/modify/approve the guidelines proposed by the project team with the leadership; \\
\cline{3-3}
                         &   & Provide advanced project management guidance and assistance; \\
\cline{3-3}
                         &   & Evaluate the design and manufacture of products to ensure that quality meets certain requirements, timely delivery and cost control. \\
\midrule
\multirow{3}{*}{\bfseries \footnotesize Blue print design} &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\
\midrule
\multirow{3}{*}{\bfseries \footnotesize Manufacturing} &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\
\midrule
\multirow{3}{*}{\bfseries \footnotesize Acceptance of delivery} &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\
\cline{2-3}
                         &   &   \\

\end{longtable}

\subsection{Product development team}



\subsection{Project Promotion Team and Coordination Group}



\subsection{Other participants and groups of the project}


\section{Responsibility matrix}

